Automatic prostate cancer detection through \acs*{dce}-\acs*{mri} images: all you need is a good normalization

### 2016-08-22 04_discussions/discussions.tex
Add the outline and the frontmatter
Finish the introduction
Add some draft discussion and conclusion

\section{Experiments and results}
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../main"
%%% End:

>>>>

\section{Discussions}\label{sec:discussions}

\begin{itemize}
  \item Discuss about the T1 parameters in Tofts and say that we can do better probably.
  \item Compare the two approach for the AIF.
  \item Make a discussion about the detailed interpretation of individual feature classification. There is something to discuss about the semi-quantitative from wash-in to wash-out reversed performance. Something also about the PUN model.
  \item Explain the drawbacks of the whole signal classification (time).
\end{itemize}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../main"
%%% End:

### 2016-08-22 05_conclusions/conclusions.tex
Add the outline and the frontmatter
Finish the introduction
Add some draft discussion and conclusion

\section{Discussions}

>>>>

\section{Conclusions and future works}\label{sec:conclusions}

In this work, we presented a new method for normalizing/standardizing \ac{dce}-\ac{mri} data.
Through different experiments, we show the benefit of such normalization.
Furthermore, we show that using the whole \ac{dce}-\ac{mri} signal instead extracting parameters lead to the best classification performance.

As avenues for future research, this normalization has to be part of a \ac{mpmri} \ac{cad} system, mixing \ac{t2w}-\ac{mri}, \ac{dce}-\ac{mri}, \ac{dw}-\ac{mri}, and \ac{mrsi}.
